### 2025-08-20 2025/Problems of Informatics/article.tex
last fix

%18
\item \label{rfa:enlit:Sergeyev2003}
Barkalov~K.A., Strongin~R.G. Metod globalnoj optimizacii s adaptivnym poryadkom proverki ogranichenij~// Zhurn. vy`chisl. matem. i matem. fiz. 2002. T.~42. No.~9. S.~1338--1350.

@@

\item \label{rfa:rulit:MonthlyBeerArticle}
Xu~N. Time Series Analysis on Monthly Beer Production in Australia~// Highlights in Science, Engineering and Technology. 2024. Vol.~94. P.~392--401. DOI: 10.54097/4z3krj13

@@

\item \label{rfa:rulit:optuna}
Akiba T., Sano S., Yanase T., Ohta T., Koyama M. Optuna: A Next-Generation Hyperparameter Optimization Framework // In Proceedings: 25th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining. 2019. P. 2623--2631. DOI: 10.1145/3292500.3330701

@@

\section*{Краткая биография}
\paragraph{Усова Марина Андреевна} -- ассистент кафедры Математического обеспечения и суперкомпьютерных технологий Института информационных технологий, математики и механики ННГУ им. Н.И. Лобачевского. Область научных интересов: модели и методы решения задач глобальной оптимизации, разработка средств визуализация данных. E-mail: usova@itmm.unn.ru. Адрес: 603022, г. Нижний Новгород, пр. Гагарина, 23.
\paragraph{Лебедев Илья Генадьевич} -- заведующий лабораторией суперкомпьютерных технологий и высокопроизводительных вычислений кафедры Математического обеспечения и суперкомпьютерных технологий Института информационных технологий, математики и механики национального исследовательского нижегородского государственного университета им. Н.И. Лобачевского, e-mail: ilya.lebedev@itmm.unn.ru. Область научных интересов: методы глобальной и локальной оптимизации, параллельные алгоритмы, программирование для графических процессоров, CUDA. Является автором и соавтором 61 научной работы.
\paragraph{Штанюк Антон Александрович} -- кандидат технических наук, доцент, доцент кафедры информатики и автоматизации научных исследований национального исследовательского нижегородского государственного университета им. Н.И. Лобачевского. E-mail: anton.shtanyuk@itmm.unn.ru. Количество печатных работ 53. Область научных интересов: моделирование и проектирование сложных систем, языки и технология программирования, обучение программированию, алгоритмы и структуры данных.
\paragraph{Баркалов Константин Александрович} -- 
доктор технических наук, доцент, заведующий кафедры Математического обеспечения и суперкомпьютерных технологий Института информационных технологий, математики и механики ННГУ им. Н.И. Лобачевского. Область научных интересов: математические модели, методы и программные средства для решения задач глобальной оптимизации; параллельные вычисления. Является автором и соавтором более 140 научных работ в указанных областях. E-mail: konstantin.barkalov@itmm.unn.ru.

@@

\paragraph{Marina Usova} -- Assistant of the Department of Mathematical Software and Supercomputer Technologies of the Institute of Information Technologies, Mathematics and Mechanics, Lobachevsky State University of Nizhny Novgorod. Research interests: models and methods for solving global optimization problems, development of data visualization tools. E-mail: usova@itmm.unn.ru. Address: 603022, Nizhny Novgorod, Gagarin Ave., 23.
\paragraph{Ilya Lebedev} -- PhD., Head of the Laboratory of Supercomputer Technologies and High-Performance Computing, Department of Mathematical Software and Supercomputing Technologies, Institute of Information Technology, Mathematics and Mechanics, Nizhny Novgorod State University. N.I. Lobachevsky. e-mail: ilya.lebedev@itmm.unn.ru. His research interests include algorithms of global and local optimization, parallel algorithms, GPU programming, CUDA. He is the author or coauthor more than 30 papers in these areas.
\paragraph{Anton Shtanyuk} -- PhD., Associate Professor at the Department of Informatics and Research Automation of the Institute of Information Technology, mathematics and mechanics at Lobachevsky State University of Nizhny Novgorod. E-mail: anton.shtanyuk@itmm.unn.ru The number of publications: 50. Research interests: modelling and design of complex systems, programming languages and technology, programming teaching, algorithms and data structures.
\paragraph{Konstantin Barkalov} -- Doctor of Technical Sciences, Professor, Head of the Department of Mathematical Software and Supercomputer Technologies, Institute of Information Technologies, Mathematics and Mechanics, Lobachevsky State University of Nizhny Novgorod. Research interests: mathematical models, methods and software for solving global optimization problems; parallel computing. E-mail: konstantin.barkalov@itmm.unn.ru.

>>>>

%18
\item \label{rfa:enlit:Sergeyev2003}
Barkalov~K.A., Strongin~R.G. Metod globalnoj optimizacii s adaptivnym poryadkom proverki ogranichenij~// Zhurn. vy`chisl. matem. i matem. fiz. 2002. T.~42, No.~9. S.~1338--1350.

@@

\item \label{rfa:rulit:MonthlyBeerArticle}
Xu~N. Time Series Analysis on Monthly Beer Production in Australia~// Highlights in Science, Engineering and Technology. 2024. Vol.~94. P.~392--401. DOI: 10.54097/4z3krj13.

@@

\item \label{rfa:rulit:optuna}
Akiba T., Sano S., Yanase T., Ohta T., Koyama M. Optuna: A Next-Generation Hyperparameter Optimization Framework // In Proceedings: 25th ACM SIGKDD International Conference on Knowledge Discovery \& Data Mining. 2019. P. 2623--2631. DOI: 10.1145/3292500.3330701.

@@

\section*{Краткая биография}
\paragraph{Усова Марина Андреевна} -- ассистент кафедры Математического обеспечения и суперкомпьютерных технологий Института информационных технологий, математики и механики ННГУ им. Н.И. Лобачевского. Область научных интересов: модели и методы решения задач глобальной оптимизации, разработка средств визуализация данных. E-mail: usova@itmm.unn.ru. Адрес: 603022, г. Нижний Новгород, пр. Гагарина, 23.
\paragraph{Лебедев Илья Генадьевич} -- заведующий лабораторией суперкомпьютерных технологий и высокопроизводительных вычислений кафедры Математического обеспечения и суперкомпьютерных технологий Института информационных технологий, математики и механики национального исследовательского нижегородского государственного университета им. Н.И. Лобачевского, Область научных интересов: методы глобальной и локальной оптимизации, параллельные алгоритмы, программирование для графических процессоров, CUDA. Является автором и соавтором 61 научной работы. E-mail: ilya.lebedev@itmm.unn.ru. 
\paragraph{Штанюк Антон Александрович} -- кандидат технических наук, доцент, доцент кафедры информатики и автоматизации научных исследований национального исследовательского нижегородского государственного университета им. Н.И. Лобачевского. Количество печатных работ 53. Область научных интересов: моделирование и проектирование сложных систем, языки и технология программирования, обучение программированию, алгоритмы и структуры данных. E-mail: anton.shtanyuk@itmm.unn.ru. 
\paragraph{Баркалов Константин Александрович} -- 
доктор технических наук, доцент, заведующий кафедры Математического обеспечения и суперкомпьютерных технологий Института информационных технологий, математики и механики ННГУ им. Н.И. Лобачевского. Область научных интересов: математические модели, методы и программные средства для решения задач глобальной оптимизации; параллельные вычисления. Является автором и соавтором более 140 научных работ в указанных областях. E-mail: konstantin.barkalov@itmm.unn.ru.

@@

\paragraph{Marina Usova} -- Assistant of the Department of Mathematical Software and Supercomputer Technologies of the Institute of Information Technologies, Mathematics and Mechanics, Lobachevsky State University of Nizhny Novgorod. Research interests: models and methods for solving global optimization problems, development of data visualization tools. E-mail: usova@itmm.unn.ru. Address: 603022, Nizhny Novgorod, Gagarin Ave., 23.
\paragraph{Ilya Lebedev} -- PhD., Head of the Laboratory of Supercomputer Technologies and High-Performance Computing, Department of Mathematical Software and Supercomputing Technologies, Institute of Information Technology, Mathematics and Mechanics, Nizhny Novgorod State University. N.I. Lobachevsky. His research interests include algorithms of global and local optimization, parallel algorithms, GPU programming, CUDA. He is the author or coauthor more than 30 papers in these areas. E-mail: ilya.lebedev@itmm.unn.ru.
\paragraph{Anton Shtanyuk} -- PhD., Associate Professor at the Department of Informatics and Research Automation of the Institute of Information Technology, mathematics and mechanics at Lobachevsky State University of Nizhny Novgorod. The number of publications: 50. Research interests: modelling and design of complex systems, programming languages and technology, programming teaching, algorithms and data structures. E-mail: anton.shtanyuk@itmm.unn.ru.
\paragraph{Konstantin Barkalov} -- Doctor of Technical Sciences, Professor, Head of the Department of Mathematical Software and Supercomputer Technologies, Institute of Information Technologies, Mathematics and Mechanics, Lobachevsky State University of Nizhny Novgorod. Research interests: mathematical models, methods and software for solving global optimization problems; parallel computing. E-mail: konstantin.barkalov@itmm.unn.ru.
